Boosting, Sparsity, and Conditional Gradient: A Tutorial

### 2014-02-19 arXiv/introduction.tex
minor tweaks to abstract and intro

The purpose of this paper is to serve as a tutorial on sparsification. While 
most of the results presented are known, they are often distributed across the 
theory, machine learning, and optimization literatures, and we hope to bring 
them all into one place, as well as to provide a unifying perspective. To start, 
we define a generalized notion of sparsity that encompasses both sparsity and 
low-rank conditions as special cases. Throughout, we will let $S$ denote a 
compact subset of $\bR^n$ and let $\Conv(S)$ denote the convex hull of $S$ 
(which will always be a closed set due to compactness of $S$). Two particularly 
important examples are:
\begin{example}
\label{ex:simplex}
Let $S$ consist of the $n$ standard unit vectors $e_1, \ldots, e_n$. Then 
$\Conv(S)$ is the $n$-dimensional simplex $\Delta_n$.
\end{example}

>>>>

The purpose of this paper is to serve as a tutorial on sparsification as it arises 
in machine learning, computer science theory, and optimization. While most of the 
results presented are known, they are often distributed across the these 
literatures. Our objective is to bring them all into one place, 
as well as to provide a unifying perspective. To start, 
we define a generalized notion of sparsity that encompasses both sparsity and 
low-rank conditions as special cases. Throughout, we will let $S$ denote a 
compact subset of $\bR^n$ and let $\Conv(S)$ denote the convex hull of $S$ 
(which will always be a closed set due to compactness of $S$). Two particularly 
important examples are:
\begin{example}
\label{ex:simplex}
Let $S$ consist of the $n$ standard unit vectors $e_1, \ldots, e_n$. Then 
$\Conv(S)$ is the $n$-dimensional simplex $\Delta_n$.
\end{example}

### 2014-02-19 arXiv/paper.tex
minor tweaks to abstract and intro

\keywords{boosting, optimization, mirror descent, Frank-Wolfe, conjugate gradient descent, herding, graph sparsification}

\begin{abstract} 
Many recent papers in machine learning and theoretical computer science have 
focused on the idea of sparse or low-rank ``approximations'' to some object: 
for instance, graph sparsification \cite{?}, low-rank SDP approximation \cite{?}, 
and pseudosampling \cite{?}. In this paper we show that, whenever presented with 
a strongly convex optimization problem whose dual problem is linear, we can obtain 
sparse approximate solutions, and use this to re-derive many of the known 
sparsification results.
% Much has been learned about herding since it was first proposed.
% We introduce a unifying framework for understanding herding and 
% related algorithms. The framework is based on a pair of optimization 
% algorithms that we call primal and dual boosted mirror descent.
% We define two classes of generalized herding algorithms, 
% including one for infinite dimensional spaces
% that may apply even when herding does not. A number 
% of convergence bounds that apply to herding and generalized
% herding are obtained. Along the way we provide
% a more cohesive picture of the connections between herding, 
% conditional gradient descent, and maximum entropy. 
\end{abstract}

>>>>

\keywords{boosting, optimization, mirror descent, Frank-Wolfe, conditional gradient descent, herding, graph sparsification}

\begin{abstract} 
Many recent papers in machine learning and theoretical computer science have 
focused on the idea of sparse or low-rank ``approximations'' to some object: 
for instance, graph sparsification \cite{?}, low-rank SDP approximation \cite{?}, 
and pseudosampling \cite{?}. In this paper we show that, whenever presented with 
a strongly convex optimization problem whose dual problem is linear, we can obtain 
sparse approximate solutions, and use this to re-derive (and in some cases 
extend) many of the known sparsification results.
% Much has been learned about herding since it was first proposed.
% We introduce a unifying framework for understanding herding and 
% related algorithms. The framework is based on a pair of optimization 
% algorithms that we call primal and dual boosted mirror descent.
% We define two classes of generalized herding algorithms, 
% including one for infinite dimensional spaces
% that may apply even when herding does not. A number 
% of convergence bounds that apply to herding and generalized
% herding are obtained. Along the way we provide
% a more cohesive picture of the connections between herding, 
% conditional gradient descent, and maximum entropy. 
\end{abstract}
